\documentclass[preprint]{aastex63}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{float}
\usepackage{natbib}
\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}

\shorttitle{Resampling of Multi-Dimensional Data}
\shortauthors{Perera}

\begin{document}


\title{An Interpolation Method for Irregularly-Sampled Multi-Dimensional Data
       Cubes}


\author{Daniel Perera}
\affil{SOFIA-USRA, NASA Ames Research Center, MS 232--12, Building N232,
       PO Box 1, Moffett Field, CA 94035--0001, USA }
\email{dperera@sofia.usra.edu}


\begin{abstract}

We present a method of interpolating irregularly-sampled multi-dimensional data
onto arbitrary coordinates using local polynomial regression.
Local regression techniques fit models to a subset of samples in the vicinity
of a given coordinate, and may optionally weight samples according to
measurement error and/or relative position, resulting in a smooth,
self-consistent function that may be evaluated over the entire sample space.
Additionally, we derive an optional method for determining local kernel
estimators in a single step, approximating an optimal reduced chi-squared
statistic on the fit.

\end{abstract}


%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

\keywords{resampling, interpolation, local polynomial regression,
          multivariate polynomials, kernel estimation}

\section{Introduction}\label{sec:introduction}
\input{introduction}

\section{Formulation}\label{sec:formulation}
\input{formulation}

\section{Implementation}\label{sec:implementation}
\input{implementation}

\section{Code Architecture}\label{sec:code-architecture}
\input{code_structure.tex}

\section{Applications}\label{sec:applications}
\input{applications}

\input{conclusions}

\acknowledgments
This work was supported by funds granted to the Universities Space Research
Association, Inc.\ (USRA) through the NASA/DLR Stratospheric Observatory for
Infrared Astronomy (SOFIA) program.
SOFIA is jointly operated by USRA under NASA contract NNA17BF53C and the
Deutsches SOFIA Institut (DSI) under DLR contract 50 OK 0901 to the University
of Stuttgart.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{}

\bibitem[Colditz et al.(2018)]{Colditz18}
Colditz S.\ et al.,\ 2018,
Spectral and Spatial Characterization and Calibration of FIFI-LS -- The Field
Imaging Spectrometer on SOFIA,
JAI, Volume 7, 1840004-(12)556

\bibitem[Fan and Gijbels(1996)]{Fan96a}
Fan, J.,\ \& Gijbels, I.\ 1996,
Local polynomial modelling and its applications,
Monographs on Statistics and Applied Probability 66 (Vol.\ 66).\ CRC Press.

\bibitem[Fan et al.(1996)]{Fan96b}
Fan, J.,\ Gijbels, I.,\ Hu, T. C.,\ \& Huang, L. S.\ 1996,
A study of variable bandwidth selection for local polynomial regression.
Statistica Sinica,\ 113--127.

\bibitem[Fischer et al.(2018)]{Fischer18}
Fischer, C.\ et al.\ 2018,
FIFI-LS: The Field-Imaging Far-Infrared Line Spectrometer on SOFIA .
JAI, 7, 1840003--556.

\bibitem[Gelman and Imbens(2019)]{Gelman19}
Gelman, A.,\ \& Imbens, G.\ 2019,
''Why high-order polynomials should not be used in regression discontinuity
designs,''
Journal of Business \& Economic Statistics,\ 37(3), 447--456.

\bibitem[Gu et al.(2015)]{Gu15}
Gu, J.,\ Li, Q.,\ \& Yang, J. C.\ 2015,
''Multivariate local polynomial kernel estimators: Leading bias and asymptotic
distribution,''
Econometric Reviews,\ 34(6--10), 979--1010.

\bibitem[Masry(1996)]{Masry1996}
Masry, E.,\ 1996,
''Multivariate local polynomial regression for time series: uniform strong
consistency and rates,''
Journal of Time Series Analysis,\ 17(6),\ 571--599.

\bibitem[Mood(1974)]{Mood1974}
Mood, A.,\ Graybill, F.,\ \& Boes, D.,\ 1974 Introduction to the Theory of
Statistics (3rd ed.).\ McGraw-Hill.\ p.\ 229.
%https://archive.org/details/introductiontoth00mood_706/page/n241/mode/2up

\bibitem[Noferini and Townsend(2016)]{Noferini2016}
Noferini, V.,\ \& Townsend, A.\ 2016,
''Numerical instability of resultant methods for multidimensional rootfinding,''
SIAM Journal on Numerical Analysis, 54(2),\ 719--743.

\bibitem[Lam and Pitrou(2015)]{Numba}
Lam,\ S.\ K.,\ Pitrou, A.,\ \& Seibert,\ S.\ (2015).
''Numba: A llvm-based python jit compiler,''
In Proceedings of the Second Workshop on the LLVM Compiler Infrastructure in HPC
(pp.\ 1--6).

\bibitem[Oliphant(2006)]{Numpy}
Oliphant,\ T.\ E.\ (2006).\ A guide to NumPy (Vol.\ 1).\ Trelgol Publishing
USA .

\bibitem[Omohundro(1989)]{Balltree}
Omohundro,\ S.\ M.,\ (1989),
''Five balltree construction algorithms,''
International Computer Science Institute Technical Report

\bibitem[Pedregosa et al.(2011)]{sklearn}
Pedregosa,\ F.\ et al.,\ 2011.
''Scikit-learn: Machine learning in Python,''
Journal of machine learning research, 12(Oct), pp.2825--2830.

\bibitem[Rossum(1995)]{Python1995}
G. van Rossum, Python tutorial, Technical Report CS-R9526,
Centrum voor Wiskunde en Informatica (CWI), Amsterdam, May 1995.

\bibitem[Stone(1977)]{Stone1977}
Stone, C.J.\ 1977,
''Consistent Nonparametric Regression,''
Ann.\ Statist.,\ vol.\ 5 (1977), 595--645

\bibitem[Vacca et al.(2020)]{Vacca20}
Vacca, W. D. et al.\ 2020,
''The Data Reduction Pipeline for FIFI-LS, the MIR Integral Field Spectrograph
for SOFIA,''
ADASS 2019

\bibitem[scikit\-image(2014)]{skimage2014}
St\'{e}fan van der Walt, Johannes L. Sch\"{o}nberger, Juan Nunez-Iglesias,
Fran\c{c}ois Boulogne, Joshua D. Warner, Neil Yager, Emmanuelle Gouillart,
Tony Yu and the scikit-image contributors.\ 2014,
''scikit-image: Image processing in Python,''
PeerJ 2:e453

\end{thebibliography}

\end{document}
